% \newglossaryentry{}
% {name=}},
% description={},
% symbol={\msrglsstyle{actor}} }


%  General Messir Glossary
\DeclareRobustCommand{\glsict}{{information and communication technological}~}

\newglossaryentry{real number}
{name={real},
sort = real,
description={name of the set of real numbers},
plural={reals},
symbol={\ensuremath{\mathbb{R}}}
}

\newglossaryentry{system operation}
{name={system operation},
description={a functionality of the system that can be triggered by a message sent by an actor belonging to the environment.},
plural={system operation},
symbol=system operation
}

\newglossaryentry{systop}
{name=system operation,
description={a functionality of the system that can be triggered by a message sent by an actor belonging to the environment.},
plural={system operations},
symbol=system operation
}

\newglossaryentry{protmod}
{name=Protocol Model,
description={},
plural={protocol models},
symbol=protocol model
}

\newglossaryentry{societics}
{name=Societics,
description={Represents the fields of hardware/software
systems used for the society extension.},
symbol=societics
}

\newglossaryentry{direct actor}
{name=direct actor,
description={an actor that interacts directly with the system. It thus belongs to the environment.},
plural={direct actors},
symbol=direct actor
}

\newglossaryentry{indirect actor}
{name=indirect actor,
description={an actor that interacts indirectly with the system through a direct actor. It thus belongs the domain but not to the environment.},
plural=indirect actors,
symbol=indirect actor
}

\newglossaryentry{abstract actor}
{name=abstract actor,
description={an actor that is not },
plural=abstract actors,
symbol=abstract actor
}

\newglossaryentry{socext}
{name=Society extension,
description={The society obtained by grouping people using natural means
extended with artificial means.},
symbol=societics
}

\newglossaryentry{usecase}
{name=Use case,
description={A use case describes a sequence of actions that provide something
of measurable value to an actor. and is drawn as a horizontal ellipse.},
symbol=Use case ,
plural=Use cases
}

\newglossaryentry{actor}
{name=actor,
description={An actor is a person, organization, or external system that plays a role in one or more interactions with the system},
plural={actors},
symbol=actor
}

\newglossaryentry{socialware}
{name={socialware},
description={Represents the software 
components used for the society extension.},
plural={socialwares},
symbol=socialware
}


