%  General Messir Glossary
\newglossaryentry{real number}
{name={real},
description={name of the set of real numbers},
plural={reals},
symbol={\ensuremath{\mathbb{R}}}
}

\newglossaryentry{systop}
{name={\msrglsstyle{system operation}},
description={a functionality of the system that can be triggered by a message sent by an actor belonging to the environment.},
plural={system operations},
symbol={\msrglsstyle{system operation}}
}

\newglossaryentry{protmod}
{name={\msrglsstyle{Protocol Model}},
description={},
plural={protocol models},
symbol={\msrglsstyle{protocol model}}
}

\newglossaryentry{societics}
{name={\msrglsstyle{Societics}},
description={Represents the fields of hardware/software
systems used for the society extension.},
symbol={\msrglsstyle{societics}}
}

\newglossaryentry{direct actor}
{name={\msrglsstyle{direct actor}},
description={an actor that interacts directly with the system. It thus belongs to the environment.},
plural={direct actors},
symbol={\msrglsstyle{direct actor}}
}

\newglossaryentry{indirect actor}
{name={\msrglsstyle{indirect actor}},
description={an actor that interacts indirectly with the system through a direct actor. It thus belongs the domain but not to the environment.},
plural={\msrglsstyle{indirect actors}},
symbol={\msrglsstyle{indirect actor}}
}

\newglossaryentry{abstract actor}
{name={\msrglsstyle{abstract actor}},
description={an actor that is not },
plural={\msrglsstyle{abstract actors}},
symbol={\msrglsstyle{abstract actor}}
}

\newglossaryentry{socext}
{name={\msrglsstyle{Society extension}},
description={The society obtained by grouping people using natural means
extended with artificial means.},
symbol={\msrglsstyle{societics}} }

\newglossaryentry{usecase}
{name={\msrglsstyle{Use case}},
description={A use case describes a sequence of actions that provide something
of measurable value to an actor. and is drawn as a horizontal ellipse.},
symbol={\msrglsstyle{Use case}} 
plural={\msrglsstyle{Use cases}} }

\newglossaryentry{actor}
{name={\msrglsstyle{actor}},
description={An actor is a person, organization, or external system that plays a role in one or more interactions with the system},
plural={actors},
symbol={\msrglsstyle{actor}}
}

\newglossaryentry{socialware}
{name={\msrglsstyle{Societics}},
description={Represents the fields of hardware/software
systems used for the society extension.},
symbol={\msrglsstyle{Societics}}
}

\newglossaryentry{system operation}
{name={system operation},
description={a functionality of the system that can be triggered by a message sent by an actor belonging to the environment.},
plural={system operation},
symbol={\msrglsstyle{system operation}}
}




% \newglossaryentry{}
% {name={\msrglsstyle{}},
% description={},
% symbol={\msrglsstyle{actor}} }
