	\subsubsection{testcase01-ts04oeAddCoordinator-actAdministrator.outactAdministrator.oeAddCoordinator}
	\label{TM-testcase01-ts04oeAddCoordinator-actAdministrator.outactAdministrator.oeAddCoordinator}

	The \msrcode{testcase01-ts04oeAddCoordinator-actAdministrator.outactAdministrator.oeAddCoordinator} has the following properties:

	\begin{teststepmodel}
		\addheading{Test Step}
		\adddoublerow{ts04oeAddCoordinator}{to test the add of a new coordinator by an administrator.}
		
		
		\addrowheading{Test Sent Message}
		\addnumberedsinglerow{TSM}{
		\vspace{-0.5cm}
		\begin{description}
			\item[] \textbf{out:TheActor}
			\item[] \textbf{sends to system}
			\item[] \textbf{\hyperlink{actAdministrator.outactAdministrator.oeAddCoordinator}{actAdministrator.outactAdministrator.oeAddCoordinator} (AdtCoordinatorID, AdtLogin, AdtPassword)}
		\end{description}}
		
		
		
		\addrowheading{Variables}
		\addnumbereddoublerow{V}{TheActor:actAdministrator}
		{actAdministor actors as being the only one allowed to add coordinators.}

		\addrowheading{Constraints}
		\addnumberedsinglerow{C}{TheActor is any \msrcode{actAdministrator} instance existing in the environment. It is expected that there exists at least one which is the same during all the test case.}
		\addnumberedsinglerow{C}{AdtCoordinatorID is equal to 1 to set the new coordinator ID}
		\addnumberedsinglerow{C}{AdtLogin has its value attribute equal to the primitive string 'steve' which is the ID defined for the new coordinator.}
		\addnumberedsinglerow{C}{AdtPassword has its value attribute equal to the primitive string 'pwdMessirExcalibur2017' which is the password to be set for steve.}


		\addrowheading{Oracle Constraints}
		\addnumberedsinglerow{OC}{the administrator should have been acknowledged for the adding of the new coordinator.}
	\end{teststepmodel}
	
	
	
		
	% ------------------------------------------
	% MCL Listing
	% ------------------------------------------
	\vspace{1cm}
	The listing~\ref{TM-testcase01-ts04oeAddCoordinator-MCL-LST} provides the \msrmessir (MCL-oriented) specification of the test step.
	
	\scriptsize
	\vspace{0.5cm}
	\begin{lstlisting}[style=MessirStyle,firstnumber=auto,captionpos=b,caption={\msrmessir (MCL-oriented) specification of the test step \emph{testcase01-ts04oeAddCoordinator}.},label=TM-testcase01-ts04oeAddCoordinator-MCL-LST]

	variables{
		TheActor : actAdministrator
		AdtCoordinatorID : dtCoordinatorID
		AdtLogin:dtLogin
		AdtPassword:dtPassword
	}
	
	constraints{
		TheActor = TheSystem.rnactAdministrator->any2(true)
		AdtCoordinatorID.value.eq('1')
		AdtLogin.value.eq('steve')
		AdtPassword.value.eq('pwdMessirExcalibur2017')
	}
	
	oracle{
		constraints{
			TheActor.inactAdministrator.ieCoordinatorAdded()
		}
	}
	
	\end{lstlisting}
	\normalsize 
	
	
