	\subsubsection{testcase01-ts09oeSollicitateCrisisHandling-actActivator.outactActivator.oeSollicitateCrisisHandling}
	\label{TM-testcase01-ts09oeSollicitateCrisisHandling-actActivator.outactActivator.oeSollicitateCrisisHandling}

	The \msrcode{testcase01-ts09oeSollicitateCrisisHandling-actActivator.outactActivator.oeSollicitateCrisisHandling} has the following properties:

	\begin{teststepmodel}
		\addheading{Test Step}
		\adddoublerow{ts09oeSollicitateCrisisHandling}{test the proactive sollication to handle an alert.}
		
		
		\addrowheading{Test Sent Message}
		\addnumberedsinglerow{TSM}{
		\vspace{-0.5cm}
		\begin{description}
			\item[] \textbf{out:TheActor}
			\item[] \textbf{sends to system}
			\item[] \textbf{\hyperlink{actActivator.outactActivator.oeSollicitateCrisisHandling}{actActivator.outactActivator.oeSollicitateCrisisHandling} ()}
		\end{description}}
		
		
		
		\addrowheading{Variables}
		\addnumbereddoublerow{V}{TheActor:icrash.environment.actActivator}
		{proactive actor responsible of triggering sollicitation functionality.}

		\addrowheading{Constraints}
		\addnumberedsinglerow{C}{TheActor is any instance existing in the current environment status. It is expected to exist at least one.}

		\addrowheading{Oracle Variables}
		\addnumbereddoublerow{OV}{TheAdministrator:actAdministrator}
			{actAdministrator actors can be sollicitated to handle alerts.}
		\addnumbereddoublerow{OV}{TheCoordinator:actCoordinator}
			{actCoordinator actors can be sollicitated to handle alerts.}
		\addnumbereddoublerow{OV}{AMessageForCrisisHandlers:ptString}
			{messages sent to sollicitated actors are of type ptString.}

		\addrowheading{Oracle Constraints}
		\addnumberedsinglerow{OC}{TheAdministrator is any instance existing in the current environment status. It is expected to exist at least one.}
		\addnumberedsinglerow{OC}{TheCoordinator is any instance existing in the current environment status. It is expected to exist at least one.}
		\addnumberedsinglerow{OC}{AMessageForCrisisHandlers is equal to the ptString 'There are alerts pending since more than the defined delay. Please REACT !'}
		\addnumberedsinglerow{OC}{TheCoordinator and TheAdministrator have received the message AMessageForCrisisHandlers.}
	\end{teststepmodel}
	
	
	
		
	% ------------------------------------------
	% MCL Listing
	% ------------------------------------------
	\vspace{1cm}
	The listing~\ref{TM-testcase01-ts09oeSollicitateCrisisHandling-MCL-LST} provides the \msrmessir (MCL-oriented) specification of the test step.
	
	\scriptsize
	\vspace{0.5cm}
	\begin{lstlisting}[style=MessirStyle,firstnumber=auto,captionpos=b,caption={\msrmessir (MCL-oriented) specification of the test step \emph{testcase01-ts09oeSollicitateCrisisHandling}.},label=TM-testcase01-ts09oeSollicitateCrisisHandling-MCL-LST]

	variables{
		TheActor : actActivator
	}
	
	constraints{
		TheActor = TheSystem.rnactActivator->any2(true)
	}
	
	oracle{
		variables{
			TheAdministrator:actAdministrator
			TheCoordinator:actCoordinator
			AMessageForCrisisHandlers:ptString
		}
		constraints{
			TheAdministrator = TheSystem.rnactAdministrator->any2(true)
			TheCoordinator = TheSystem.rnactCoordinator->any2(true)
			AMessageForCrisisHandlers = 'There are alerts pending since more than the defined delay. Please REACT !'
			TheAdministrator.inactAdministrator.ieMessage(AMessageForCrisisHandlers)
			TheCoordinator.inactAdministrator.ieMessage(AMessageForCrisisHandlers)
		}
	}
	
	\end{lstlisting}
	\normalsize 
	
	
