	\subsubsection{testcase01-ts07oeAlert1-actComCompany.outactComCompany.oeAlert}
	\label{TM-testcase01-ts07oeAlert1-actComCompany.outactComCompany.oeAlert}

	The \msrcode{testcase01-ts07oeAlert1-actComCompany.outactComCompany.oeAlert} has the following properties:

	\begin{teststepmodel}
		\addheading{Test Step}
		\adddoublerow{ts07oeAlert1}{tests the declaration of a new alert functionality.}
		
		
		\addrowheading{Test Sent Message}
		\addnumberedsinglerow{TSM}{
		\vspace{-0.5cm}
		\begin{description}
			\item[] \textbf{out:TheActor}
			\item[] \textbf{sends to system}
			\item[] \textbf{\hyperlink{actComCompany.outactComCompany.oeAlert}{actComCompany.outactComCompany.oeAlert} (AetHumanKind, AdtDate, AdtTime, AdtPhoneNumber, AdtGPSLocation, AdtComment)}
		\end{description}}
		
		
		
		\addrowheading{Variables}
		\addnumbereddoublerow{V}{TheActor:actComCompany}
		{actComCompany actors transfer alert declaration messages.}

		\addrowheading{Constraints}
		\addnumberedsinglerow{C}{TheActor is any instance existing in the current environment status. It is expected to exist at least one.}
		\addnumberedsinglerow{C}{AetHumanKind is equal to witness}
		\addnumberedsinglerow{C}{AdtDate is equal to the 26th of November 2017}
		\addnumberedsinglerow{C}{AdtTime is equal to 10:10:16 using a 24-hours.}
		\addnumberedsinglerow{C}{AdtPhoneNumber is equal to the ptString value '+3524666445252'.}
		\addnumberedsinglerow{C}{AdtGPSLocation is equal to (49.627675 , 6.159590).}
		\addnumberedsinglerow{C}{AdtComment is equal to '3 cars involved in an accident.'}


		\addrowheading{Oracle Constraints}
		\addnumberedsinglerow{OC}{AdtSMS is equal to the ptString 'Your alert has been registered. We will handle it and keep you informed'.}
		\addnumberedsinglerow{OC}{AdtSMS is sent to the phone number AdtPhoneNumber using the communication company having sent the alert using its ieSmsSend input message.}
	\end{teststepmodel}
	
	
	
		
	% ------------------------------------------
	% MCL Listing
	% ------------------------------------------
	\vspace{1cm}
	The listing~\ref{TM-testcase01-ts07oeAlert1-MCL-LST} provides the \msrmessir (MCL-oriented) specification of the test step.
	
	\scriptsize
	\vspace{0.5cm}
	\begin{lstlisting}[style=MessirStyle,firstnumber=auto,captionpos=b,caption={\msrmessir (MCL-oriented) specification of the test step \emph{testcase01-ts07oeAlert1}.},label=TM-testcase01-ts07oeAlert1-MCL-LST]

	variables{
		TheActor : actComCompany
		AetHumanKind:etHumanKind
		AdtDate:dtDate
		AdtTime:dtTime
		AdtPhoneNumber:dtPhoneNumber
		AdtGPSLocation:dtGPSLocation
		AdtComment:dtComment
	}
	
	constraints{
		TheActor = TheSystem.rnactComCompany->any2(true)
		AetHumanKind = witness
		AdtDate.year.value = 2017
		AdtDate.month.value = 11
		AdtDate.day.value = 26
		AdtTime.hour.value = 10
		AdtTime.minute.value = 10
		AdtTime.second.value = 16
		AdtPhoneNumber.value = '+3524666445252'
		AdtGPSLocation.latitude.value = 49.627675
		AdtGPSLocation.longitude.value = 6.159590
		AdtComment.value = '3 cars involved in an accident.'
	}
	
	oracle{
		variables{
			AdtSMS:dtSMS
		}
		constraints{
			AdtSMS.value = 'Your alert has been registered. We will handle it and keep you informed'
			TheActor.inactComCompany.ieSmsSend(AdtPhoneNumber,AdtSMS)
		}
	}
	
	\end{lstlisting}
	\normalsize 
	
	
