\subsection{\msrcode{actAdministrator} Actor}


\begin{actortable}
	\addheading{Actor}
	
	\adddoublerow{actAdministrator}{represents an actor responsible of administration tasks for the \msricrash system.}
	
	\addrowheading{Extends}
	\addsinglerow{icrash.environment.actAuthenticated}
	
	
	
	\addrowheading{Operations}
	\adddoublerow{\msrcode{init():ptBoolean}}{ }
	\adddoublerow{\msrcode{oegetStatistic():ptBoolean}}{ }
	
	

	\addrowheading{OutputInterfaces}
	\addnumbereddoublerow{OUT}{\hypertarget{actAdministrator.outactAdministrator.oeAddCoordinator}
			{\msrcode{oeAddCoordinator(AdtCoordinatorID:dtCoordinatorID, AdtLogin:dtLogin, AdtPassword:dtPassword):ptBoolean}}}
			{sent to add a new coordinator in the system's post state and environment's post state.}
	\addnumbereddoublerow{OUT}{\hypertarget{actAdministrator.outactAdministrator.oeDeleteCoordinator}
			{\msrcode{oeDeleteCoordinator(AdtCoordinatorID:dtCoordinatorID):ptBoolean}}}
			{sent to delete an existing coordinator in the system's post state and environment's post state.}
	\addnumbereddoublerow{OUT}{\hypertarget{actAdministrator.outactAdministrator.oegetstatisticUser}
			{\msrcode{oegetstatisticUser(statisticUser:dtgetStatisticUserActivity):ptBoolean}}}
			{ send the statistic for the user activity with the time.}
	\addnumbereddoublerow{OUT}{\hypertarget{actAdministrator.outactAdministrator.oegetstatisticCrises}
			{\msrcode{oegetstatisticCrises(statisticCrises:dtgetStatisticCrisisinTime):ptBoolean}}}
			{ send the statistic for the number of sending crises  with the time.}
	\addnumbereddoublerow{OUT}{\hypertarget{actAdministrator.outactAdministrator.oegetstatisticTypesOfCrises}
			{\msrcode{oegetstatisticTypesOfCrises(statisticTypes:dtgetStatisticTypeCrisis):ptBoolean}}}
			{ send the statistic for the average time of the 3 different types of a cries.}
	
	\addrowheading{InputInterfaces}
	\addnumbereddoublerow{IN}{\msrcode{ieCoordinatorAdded():ptBoolean}}
							 {its reception confirms the creation of the requested coodinator. }
	\addnumbereddoublerow{IN}{\msrcode{ieCoordinatorDeleted():ptBoolean}}
							 {its reception confirms the deletion of the requested coodinator. }
	\addnumbereddoublerow{IN}{\msrcode{iegetStatistic():ptBoolean}}
							 {It show the statistic }
	
\end{actortable}
