\subsection{Primary types - Datatypes types descriptions}





The table below is providing comments on the graphical views given for the datatype types of the primary types.


\begin{datadictionary}
\addheading{Datatypes}

\adddoublerow{dtAlertID}{ A string used to identify alerts.}
\addsingletwocolumnrow{extends}{dtString}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which strings are considered as valid alert identifiers.}
\adddoublerow{dtCaptcha}{Contains the actual representation of an image based captcha test}
\adddoubletwocolumnrow{attribute}{\msrcode{id: dtCaptchaId}}{The internal id of this captcha test. This is used for the actCaptchaGenerator to identify the captcha test in case of a response.}
\adddoubletwocolumnrow{attribute}{\msrcode{question: ptString}}{The human readable question related to this captcha test, needed by a human to be able to solve the captcha test}
\adddoublerow{dtCaptchaId}{}
\addsingletwocolumnrow{extends}{dtInteger}
\adddoublerow{dtCaptchaImage}{The actual representation of an image related to a captcha test. The inheritance from dtString allows to store the binary data of the image as bytes in string format.}
\addsingletwocolumnrow{extends}{dtString}
\adddoubletwocolumnrow{attribute}{\msrcode{height: dtInteger}}{Represents the height of the image in pixels}
\adddoubletwocolumnrow{attribute}{\msrcode{width: dtInteger}}{Represents the width of the image in pixels}
\adddoublerow{dtCaptchaResponse}{Contains the users response to a given captcha test}
\adddoubletwocolumnrow{attribute}{\msrcode{id: dtCaptchaId}}{The internal id which qualifies the related captcha test}
\adddoubletwocolumnrow{attribute}{\msrcode{response: ptString}}{The response data given by the user}
\adddoublerow{dtCaptchaResponseMap}{A data structure which hold references to correct answers, each one related to one captcha test. This data structure maps an id number to at last one answer.}
\adddoubletwocolumnrow{operation}{\msrcode{get(AId:dtCaptchaId):dtCaptchaResponse}}{Gets the answer of the mapping from the given id}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{Verifies if this map is a valid data structure}
\adddoubletwocolumnrow{operation}{\msrcode{register(AdtResponse:dtCaptchaResponse):ptBoolean}}{Saves an answer to a captcha test to this data structure}
\adddoubletwocolumnrow{operation}{\msrcode{remove(AId:dtCaptchaId):ptBoolean}}{Removes the reference to an answer from this data structure by the given id number}
\adddoublerow{dtComment}{a datatype made of a string value used to receive,store and send textual information about crisis and alerts.}
\addsingletwocolumnrow{extends}{dtString}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which strings are considered as valid comments.}
\adddoublerow{dtCoordinatorID}{A string used to identify coordinators.}
\addsingletwocolumnrow{extends}{dtString}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which strings are considered as valid coordinators identifiers.}
\adddoublerow{dtCrisisID}{ A string used to identify crisis.}
\addsingletwocolumnrow{extends}{dtString}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which strings are considered as valid crisis identifiers.}
\adddoublerow{dtGPSLocation}{used to define coordinates of geograpical positions on earth. It is defined a couple made of a latitude and a longitude.}
\adddoubletwocolumnrow{attribute}{\msrcode{latitude: dtLatitude}}{for the latitude part of the coordinate.}
\adddoubletwocolumnrow{attribute}{\msrcode{longitude: dtLongitude}}{for the longitude part of the coordinate.}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which couples are considered as valid dtGPSLocation values.}
\adddoubletwocolumnrow{operation}{\msrcode{isNearTo(AGPSLocation:dtGPSLocation):ptBoolean}}{used to determine if locations are considered enough close to be treated as equivalent in the application domain context.}
\adddoublerow{dtLatitude}{used to define a latitude value of a geograpical positions on earth.}
\addsingletwocolumnrow{extends}{dtReal}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which strings are considered as valid dtLatitude.}
\adddoublerow{dtLogin}{ a login string used to authentify an \msricrash user}
\addsingletwocolumnrow{extends}{dtString}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which strings are considered as valid dtLogin.}
\adddoublerow{dtLongitude}{used to define a longitude value of a geograpical positions on earth. }
\addsingletwocolumnrow{extends}{dtReal}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which strings are considered as valid dtLongitude.}
\adddoublerow{dtPassword}{a password string used to authentify an \msricrash user}
\addsingletwocolumnrow{extends}{dtString}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which strings are considered as valid dtPassword.}
\adddoublerow{dtPhoneNumber}{a string used to store the phone number from the human declaring the crisis or the alert.}
\addsingletwocolumnrow{extends}{dtString}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which strings are considered as valid dtPhoneNumber.}
\adddoublerow{dtStatisticCrisisinTime}{Statistic representing a number of crises compared with a specific timespan}
\adddoubletwocolumnrow{attribute}{\msrcode{number: ptInteger}}{The amount of crises}
\adddoubletwocolumnrow{attribute}{\msrcode{time: dtTime}}{The related timestamp}
\adddoublerow{dtStatisticTypeCrisis}{Show what the attribute for the static the average time of the different crises}
\adddoubletwocolumnrow{attribute}{\msrcode{time: dtTime}}{The related timestamp representing the date}
\adddoubletwocolumnrow{attribute}{\msrcode{typeC: ptString}}{The type of the crisis}
\adddoublerow{dtStatisticUserActivity}{Represents a statistic of a number of users in relation to a specific timespan}
\adddoubletwocolumnrow{attribute}{\msrcode{number: ptInteger}}{The amount of involved users}
\adddoubletwocolumnrow{attribute}{\msrcode{time: dtTime}}{The related timestamp}
\end{datadictionary}


\begin{datadictionary}
\addheading{Enumerations}

\adddoublerow{etAlertStatus}{
this type is used to indicate the different validation status of an alert.
}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which litteral belongs to the enumeration.}
\adddoublerow{etCrisisStatus}{
this type is used to indicate the different handling status of a crisis.
}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which litteral belongs to the enumeration.}
\adddoublerow{etCrisisType}{
this type is used to indicate the different types of a crisis.
}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which litteral belongs to the enumeration.}
\adddoublerow{etHumanKind}{
this type is used to indicate the kind of human that informs about a car crash crisis.
}
\adddoubletwocolumnrow{operation}{\msrcode{is():ptBoolean}}{used to determine which litteral belongs to the enumeration.}
\end{datadictionary}





