\subsection{Primary types - Class types descriptions}




The table below is providing comments on the graphical views given for the class types of the primary types. Type logical operations are precisely specified in the operation model.

\begin{datadictionary}
\addheading{Classes}

\adddoublerow{ctAdministrator}{used to caracterize internally the entity that is responsible of administrating the \msricrash system.}
\addsingletwocolumnrow{extends}{icrash.concepts.primarytypes.classes.ctAuthenticated}
\adddoubletwocolumnrow{operation}{\msrcode{init(Alogin:dtLogin, Apwd:dtPassword):ptBoolean}}{used to initialize the current object as a new instance of the ctAdministrator type.}
\adddoublerow{ctAlert}{Used to model crisis alerts sent by any human having communication capability using communication companies belonging to the system's environment}
\adddoubletwocolumnrow{attribute}{\msrcode{comment: dtComment}}{a textual description providing unstructured information on the alert.}
\adddoubletwocolumnrow{attribute}{\msrcode{id: dtAlertID}}{the alert unique identification information.}
\adddoubletwocolumnrow{attribute}{\msrcode{instant: dtDateAndTime}}{the date and time at which the alert notification has been sent.}
\adddoubletwocolumnrow{attribute}{\msrcode{location: dtGPSLocation}}{the position of the alert provided by the space-based satellite navigation system used by the human using the communication company to inform the \msricrash system of a crisis.}
\adddoubletwocolumnrow{attribute}{\msrcode{status: etAlertStatus}}{the alert validation status }
\adddoubletwocolumnrow{operation}{\msrcode{init(Aid:dtAlertID, Astatus:etAlertStatus, Alocation:dtGPSLocation, Ainstant:dtDateAndTime, Acomment:dtComment):ptBoolean}}{used to initialize the current object as a new instance of the ctAlert type.}
\adddoubletwocolumnrow{operation}{\msrcode{isSentToCoordinator(AactCoordinator:actCoordinator):ptBoolean}}{used to provide a given coordinator with current alert information.}
\adddoublerow{ctAuthenticated}{used to model system's representation about actors that need to authenticate to access some specific functionalities.}
\adddoubletwocolumnrow{attribute}{\msrcode{login: dtLogin}}{an identifier for authentication.}
\adddoubletwocolumnrow{attribute}{\msrcode{pwd: dtPassword}}{a key for authentication.}
\adddoubletwocolumnrow{attribute}{\msrcode{vpIsLogged: ptBoolean}}{used to determine the access status.}
\adddoubletwocolumnrow{operation}{\msrcode{init(Alogin:dtLogin, Apwd:dtPassword):ptBoolean}}{used to initialize the current object as a new instance of the ctAuthenticated type.}
\adddoublerow{ctCoordinator}{used to model system's representation about the actors that have the responsibility to handle alerts and crisis.}
\addsingletwocolumnrow{extends}{icrash.concepts.primarytypes.classes.ctAuthenticated}
\adddoubletwocolumnrow{attribute}{\msrcode{id: dtCoordinatorID}}{a unique identification information.}
\adddoubletwocolumnrow{operation}{\msrcode{init(Aid:dtCoordinatorID, Alogin:dtLogin, Apwd:dtPassword):ptBoolean}}{used to initialize the current object as a new instance of the ctCoordinator type.}
\adddoublerow{ctCrisis}{Used to model crisis that are infered from the reception of at least one alert message. Crisis aer entities that are handled by the \msricrash system.}
\adddoubletwocolumnrow{attribute}{\msrcode{comment: dtComment}}{a textual description providing unstructured information on the crisis handling.}
\adddoubletwocolumnrow{attribute}{\msrcode{id: dtCrisisID}}{the crisis unique identification information.}
\adddoubletwocolumnrow{attribute}{\msrcode{instant: dtDateAndTime}}{the date and time at which the first related alert notification has been sent.}
\adddoubletwocolumnrow{attribute}{\msrcode{location: dtGPSLocation}}{the position of the crisis equal by the one of the first alert received and associated to the crisis.}
\adddoubletwocolumnrow{attribute}{\msrcode{status: etCrisisStatus}}{the crisis handling status.}
\adddoubletwocolumnrow{attribute}{\msrcode{type: etCrisisType}}{an indication of the gravity of the crisis.}
\adddoubletwocolumnrow{operation}{\msrcode{handlingDelayPassed():ptBoolean}}{used to determine if the crisis stood too longly in a pending status since last reminder.}
\adddoubletwocolumnrow{operation}{\msrcode{init(Aid:dtCrisisID, Atype:etCrisisType, Astatus:etCrisisStatus, Alocation:dtGPSLocation, Ainstant:dtDateAndTime, Acomment:dtComment):ptBoolean}}{used to initialize the current object as a new instance of the ctAlert type.}
\adddoubletwocolumnrow{operation}{\msrcode{isAllocatedIfPossible():ptBoolean}}{used to allocate a crisis to a coordinator if any or to alert the administrator of crisis waiting to be handled.}
\adddoubletwocolumnrow{operation}{\msrcode{isSentToCoordinator(AactCoordinator:actCoordinator):ptBoolean}}{used to provide a given coordinator with current crisis information.}
\adddoubletwocolumnrow{operation}{\msrcode{maxHandlingDelayPassed():ptBoolean}}{used to determine if the crisis stood too longly in a pending status since its creation.}
\adddoublerow{ctHuman}{used to model system's representation about the indirect actors that has alerted of potential crisis.}
\adddoubletwocolumnrow{attribute}{\msrcode{id: dtPhoneNumber}}{the number of the communication device used to send an alert to \msricrash system.}
\adddoubletwocolumnrow{attribute}{\msrcode{kind: etHumanKind}}{role with respect to the alert notified.}
\adddoubletwocolumnrow{operation}{\msrcode{init(Aid:dtPhoneNumber, Akind:etHumanKind):ptBoolean}}{\msrcode{init}: used to initialize the current object as a new instance of the ctHuman type.}
\adddoublerow{ctState}{used to model the system. Each system specified using \msrmessir must include a ctState class for which there is only one instance at any state of the abstract machine after creation.}
\adddoubletwocolumnrow{attribute}{\msrcode{clock: dtDateAndTime}}{used to represent the system local time.}
\adddoubletwocolumnrow{attribute}{\msrcode{crisisReminderPeriod: dtSecond}}{used to define the delay between two reminders after which a reminder must be sent to the administrator and to the known coordinators to encourage them to handle the crisis.}
\adddoubletwocolumnrow{attribute}{\msrcode{maxCrisisReminderPeriod: dtSecond}}{used to define the maximum delay after which the crisis is ramdomly allocated to a coordinator if any or an alert message is sent to the administrator in order to encourage him to add coordinators.}
\adddoubletwocolumnrow{attribute}{\msrcode{nextValueForAlertID: dtInteger}}{\msrcode{nextValueForAlertID: dtInteger}: used to associate each alert declared with a unique idenitification value. }
\adddoubletwocolumnrow{attribute}{\msrcode{nextValueForCrisisID: dtInteger}}{used to associate each crisis declared with a unique idenitification value. }
\adddoubletwocolumnrow{attribute}{\msrcode{vpLastReminder: dtDateAndTime}}{date and time of the last reminder.}
\adddoubletwocolumnrow{attribute}{\msrcode{vpStarted: ptBoolean}}{used to avoid reacting to an actor message if the system is not started (i.e. oeCreateSystemAndEnvironment not executed).}
\adddoubletwocolumnrow{operation}{\msrcode{init(AnextValueForAlertID:dtInteger, AnextValueForCrisisID:dtInteger, Aclock:dtDateAndTime, AcrisisReminderPeriod:dtSecond, AmaxCrisisReminderPeriod:dtSecond, AvpLastReminder:dtDateAndTime, AvpStarted:ptBoolean):ptBoolean}}{used to initialize the current object as a new instance of the ctState type.}
\end{datadictionary}
