\subsection{Operation Model for oeAddCoordinator}

\label{OM-oeAddCoordinator}


The \msrcode{oeAddCoordinator} operation has the following properties:

	\begin{operationmodel}
	\addheading{Operation}
	\adddoublerow{oeAddCoordinator}{sent to add a new coordinator in the system's post state and environment's post state.}

	\addrowheading{Parameters}
	\addnumbereddoublerow{}{AdtCoordinatorID: dtCoordinatorID}{used to initialize the id field} 
	\addnumbereddoublerow{}{AdtLogin: dtLogin}{used to initialize the login field} 
	\addnumbereddoublerow{}{AdtPassword: dtPassword}{used to initialize the password field} 

	\addrowheading{Return type}
	\addsinglerow{ptBoolean}

	\addrowheading{Pre-Condition (protocol)}
	\addnumberedsinglerow{PreP}{the system is started}
	\addnumberedsinglerow{PreP}{the actor logged previously and did not log out ! (i.e. the associated ctAdministrator instance is considered logged)}
		
	\addrowheading{Pre-Condition (functional)}
	\addnumberedsinglerow{PreF}{ it is supposed that there cannot exist a ctCoordinator instance with the same \msrcode{id} attribute as the one the administrator wants to delete.}

	\addrowheading{Post-Condition (functional)}
	\addnumberedsinglerow{PostF}{ the environment has a new instance of coordinator actor allowing for input/output message communication with the system.}
	\addnumberedsinglerow{PostF}{the system's state has a new instance of ctCoordinator initialized with the given values.}
	\addnumberedsinglerow{PostF}{the new actor instance and ctCoordinator instance are related.}
	\addnumberedsinglerow{PostF}{the new actor instance and ctCoordinator instance are related according to the authenticated association.}
	\addnumberedsinglerow{PostF}{the administrator actor is informed about the satisfaction of its request.}

	\addrowheading{Post-Condition (protocol)}
	\addnumberedsinglerow{PostP}{ none}
	\end{operationmodel}



	% ------------------------------------------
	% MCL Listing
	% ------------------------------------------
	\vspace{1cm}
	The listing~\ref{OM-actAdministrator-oeAddCoordinator-MCL-LST} provides the \msrmessir (MCL-oriented) specification of the operation.
	
	\scriptsize
	\vspace{0.5cm}
	\begin{lstlisting}[style=MessirStyle,firstnumber=auto,captionpos=b,caption={\msrmessir (MCL-oriented) specification of the operation \emph{oeAddCoordinator}.},label=OM-actAdministrator-oeAddCoordinator-MCL-LST]

	/* Pre Protocol:*/ 
	preP{let TheSystem: ctState in
	  let TheActor:actAdministrator in
	  
	  self.rnActor.rnSystem = TheSystem
	  and self.rnActor = TheActor
	  
	/* PreP01 */
	  and TheSystem.vpStarted = true
	/* PreP02 */
	  and TheActor.rnctAuthenticated.vpIsLogged = true}
	
	/* Pre Functional:*/
	preF{let TheSystem: ctState in
	  let TheActor:actAdministrator in
	  let ColctCoordinators:Bag(ctCoordinator) in
	  
	  self.rnActor.rnSystem = TheSystem
	  and self.rnActor = TheActor
	/* PreF01 */
	  and TheSystem.rnctCoordinator->select(id.eq(AdtCoordinatorID))
	      = ColctCoordinators
	  and ColctCoordinators->isEmpty() = true}
	
	/* Post Functional:*/ 
	postF{let TheSystem: ctState in
	  let TheactCoordinator:actCoordinator in
	  let ThectCoordinator:ctCoordinator in
	  self.rnActor.rnSystem = TheSystem
	  and self.rnActor = TheActor
	/* PostF01 */
	  TheactCoordinator.init()
	/* PostF02 */
	  and ThectCoordinator.init(AdtCoordinatorID,AdtLogin,AdtPassword)
	
	/* PostF03 */
	  and TheactCoordinator@post.rnctCoordinator = ThectCoordinator
	  
	/* PostF04 */  
	  and ThectCoordinator@post.rnactAuthenticated = TheactCoordinator
	   
	/* PostF05 */  
	  and TheActor.rnInterfaceIN^ieCoordinatorAdded()}
	
	/* Post Protocol:*/ 
	postP{ true}
	
	\end{lstlisting}
	\normalsize 
	
	
	
	





